Composition-climate paper

### 2015-05-04 Composition_Ecology.Rmd
Minor changes.

ggplot(all.hellinger, aes(x = fixedv_c, y = fixedc_v, color = climate)) +
  geom_point() + geom_abline(intercept=0, slope = 1) + facet_wrap(~shift) +
  xlab('Vegetation Fixed - Climate Shifting') +
  ylab('Climate Fixed - Vegetation Shifting') +
  theme_bw()

>>>>

ggplot(all.hellinger, aes(x = fixedv_c, y = fixedc_v, color = climate)) +
  geom_point(size = 2) + geom_abline(intercept=0, slope = 1) + facet_wrap(~shift) +
  xlab('Vegetation Fixed - Climate Shifting') +
  ylab('Climate Fixed - Vegetation Shifting') +
  theme_bw()
